\documentclass[11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\geometry{
  letterpaper,
  left=1in,
  right=1in,
  top=1in,
  bottom=1in
}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
\usepackage[english]{babel}

\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}

\begin{document}

\begin{flushright}
\today
\end{flushright}

\vspace{0.5in}

\begin{flushleft}
Hiring Manager \\
CloudRedux \\
Pune, Maharashtra
\end{flushleft}

\vspace{0.3in}

Dear Hiring Manager,

I am writing to express my strong interest in the Junior AI/LLM Engineer position at CloudRedux. As a Computer Science Pre Final year student at the Indian Institute of Information Technology, Vadodara, I am enthusiastic about exploring the world of Artificial Intelligence and large language models. Your organization's focus on breaking boundaries and embracing the latest technologies resonates deeply with my passion for AI and machine learning, and I am eager to contribute to innovative AI-driven solutions that drive change and truly matter.

I have hands-on experience developing LLM-driven solutions, RAG workflows, and conversational AI systems using Python. At ComputeLib, I developed LLM-based AI agents and conversational AI workflows, contributing to domain-specific agent frameworks supporting multi-turn conversations powered by LLMs. I assisted in developing scalable AI systems and RAG workflows, participated in evaluating conversational AI pipelines, and helped identify system limitations to recommend improvements. At FadFocus, I developed AI-powered features using Python and LLM integrations, implementing conversational AI workflows and deploying AI frameworks in cloud-based environments using Docker. My project experience includes StackIt, an AI-moderated Q\&A platform with 95\% detection accuracy, VocaLingo, a real-time translation app enabling multi-turn, multi-modal conversations across 40+ languages, and AutoPrep.ai, an AI-powered study assistant using vector embeddings and RAG workflows. I have practical experience with Python, JavaScript, React.js, Node.js, Docker, Git, and IDE tools including Visual Studio Code, PyCharm, and Jupyter Notebooks, along with exposure to conversational AI technologies, NLP, and dialogue systems.

I am a problem solver with a collaborative attitude and a strong desire to learn and grow in the fields of AI and machine learning. I am eager to work alongside experienced engineers to develop and enhance AI frameworks and systems, assist in developing scalable LLM-driven RAG workflows, and participate in code development, design reviews, and testing processes with opportunities for mentorship and learning. I believe my technical skills, project experience related to AI and NLP, and alignment with CloudRedux's mission to create solutions that drive change make me a strong fit for this internship. Thank you for considering my application, and I look forward to the opportunity to discuss how I can contribute to your dynamic team and grow with CloudRedux.

\vspace{0.3in}

Sincerely, \\
Sivajeet Sabdakar \\
+91 7217-556-581 \\
\href{mailto:sivajeetsabdakar@gmail.com}{sivajeetsabdakar@gmail.com} \\
\href{https://linkedin.com/in/sivajeet-sabdakar-5a03aa278}{linkedin.com/in/sivajeet-sabdakar} \\
\href{https://github.com/sivajeetsabdakar}{github.com/sivajeetsabdakar}

\end{document}

