%-----------PROJECTS-----------%
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{StackIt: AI-Moderated Q\&A Platform} \\ \emph{Python, Machine Learning, Natural Language Processing, Computer Vision, Scalable Systems}}
{\href{https://github.com/sivajeetsabdakar/Odoo-dors}{[Source Code]}}
\resumeItemListStart
    \resumeItem{Engineered a scalable microservice architecture during a \textbf{Hackathon}, handling \textbf{500+} concurrent requests, and integrated \textbf{NLP} and \textbf{CV} pipelines to automate content filtering with \textbf{95\% detection accuracy} for toxic text and unsafe media.}
    \resumeItem{Implemented \textbf{Cloudinary} workflows with configurable thresholds for precise content moderation with customizable sensitivity settings.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Flinder: AI-Powered Flatmate Matcher} \\ \emph{Python, Machine Learning, Vector Embeddings, Scalable Systems}}
{\href{https://github.com/OmDixit2107/Flinder}{[Source Code]}}
\resumeItemListStart
    \resumeItem{Secured a \textbf{Hackathon Victory} by architecting a recommendation engine with \textbf{vector embeddings}, validated through user acceptance testing, and leveraged \textbf{Supabase} for real-time sync with data retrieval latency under \textbf{50ms}.}
    \resumeItem{Deployed optimized APIs for a \textbf{Flutter} frontend with efficient caching strategies, enabling instant chat capabilities and improved responsiveness.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{HawkeRoute: Smart Hawker Route System} \\ \emph{Python, Scalable Systems, Distributed Systems}}
{\href{https://github.com/sivajeetsabdakar/HawkeRoute}{[Source Code]}}
\resumeItemListStart
    \resumeItem{Developed an asynchronous backend using \textbf{Celery} and \textbf{Redis} to process \textbf{1,000+} daily background tasks for dynamic routing, and designed optimized \textbf{SQL} schemas with strategic indexing to handle complex transactions efficiently.}
    \resumeItem{Integrated \textbf{Twilio} for automated SMS alerts and built backend support for \textbf{live tracking} visualization, enabling real-time logistics coordination and dynamic route optimization for urban delivery operations.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{VocaLingo: Real-Time Translation App} \\ \emph{Python, Natural Language Processing, Scalable Systems}}
{\href{https://github.com/sivajeetsabdakar/Vocalingo}{[Source Code]}}
\resumeItemListStart
    \resumeItem{Engineered a custom \textbf{stereo audio routing} system to isolate input/output channels and orchestrated real-time \textbf{STT} and \textbf{TTS} data streams with multi-threading, enabling simultaneous bi-directional conversation across \textbf{40+ languages} with synchronized audio processing.}
    \resumeItem{Deployed a self-hosted \textbf{LibreTranslate} instance via \textbf{Docker}, eliminating API rate limits and reducing translation latency to under \textbf{200ms} for fluid live interpretation.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Digit Recognition Neural Network} \\ \emph{Python, Machine Learning, Deep Learning, NumPy}}
{\href{https://github.com/sivajeetsabdakar/NeuralNetwork_DigitRecognition}{[Source Code]}}
\resumeItemListStart
    \resumeItem{Constructed a \textbf{Feedforward Neural Network} processing \textbf{60,000} MNIST images, implementing backpropagation from scratch, and achieved \textbf{97\% classification accuracy} by fine-tuning hyperparameters and optimizing weight initialization strategies.}
    \resumeItem{Utilized \textbf{Matplotlib} for diagnostics, improving model convergence speed by \textbf{2x} through visualized loss function analysis.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AutoPrep.ai (formerly Class Buddy)} \\ \emph{Python, Machine Learning, Vector Embeddings, Natural Language Processing}}
{\href{https://github.com/sivajeetsabdakar/AutoPrep.ai}{[Source Code]}}
\resumeItemListStart
    \resumeItem{Secured a \textbf{3rd position at HackTheMoutains 5.0} by building a question-similarity engine using \textbf{vector embeddings} (BERT/TF-IDF) to recommend personalized practice questions based on historical exam patterns.}
    \resumeItem{Developed custom \textbf{NLP} pipelines to analyze historical exam datasets, identifying key question patterns with \textbf{90\%+ precision} and automating study material curation.}
\resumeItemListEnd

\resumeSubHeadingListEnd